%%%% Weekly Report Information %%%%
\newcommand{\handoutName}{Weekly report}
\newcommand{\handoutdate}{\today}
%\newcommand{\duedate}{}
\input{Header.tex}

\section{My \emph{Objectives} this week}
\begin{itemize}
\item Loading windows on my Macbook
\item Running Kilobots with windows
\item Writing and simulating the algorithm of setting positions for two robots
\item Adding a folder for Journal version of our IROS papers
\end{itemize}


\section{Two Robots Positioning}\label{sec:algorithm}


\subsection{Controlling Covariance}

In this algorithm we want to control two position of two robots using friction. For ease of proof, we assume that we want to \emph{x} position of the robots, and \emph{y} of the robots are not the same and will remain the initial $\Delta y $ as we go through the algorithm.
\begin{algorithm}
\caption{Getting desired X-space}\label{alg:XControl}
\begin{algorithmic}[1]
\Require Knowledge of the starting and ending positions  of the two robots $s_1$ (topper robot) \& $s_2$ (lower robot)  \& $e_1$  \& $e_2$  and $L$ length of the bottom wall. Current position of the robot will be showed as $r$.
\Ensure $\Delta y(t) = \delta y(0)$ 
\State $e_{1x} - e_{2x} = \Delta e_x$
\State $s_{1x} - s_{2x} = \Delta s_x$
\If {$\Deltae < 0 $ }
\State Move almost to right wall
\Else Move almost to left wall
\EndIf
\State Move to bottom
\If $\Delta e - \Delta x > 0 $
\State Update current position of the robots: $r_1$ , $r_2$
\State Go right for $min(\|\Delta e - \Delta x \|, L- r_1)$
\Else Go left for $-min(\|\Delta e - \Delta x \|, r_1)$
\EndIf 
\State Move $\epsilon$ up
\State Update current position of the robots: $r_1$ , $r_2$
\If $\Delta r_x = \Delta e_x$ 
\State Go to $e_1$, $e_2$
\State Return
\Else Do the algorithm again with the inputs of $r_1$, $r_2$, $e_1$, $e_2$
\EndIf



\end{algorithmic}
\end{algorithm}


\section{My \emph{Accomplishments} this week}

\subsection{\emph{Kilobots}}

\begin{itemize}
\item I installed windows on my machine, and was able to see robots moving around and also communicating with each other.
\end{itemize}

\subsection{\emph{Algorithms}}

\begin{itemize}
\item I wrote the algorithm with latex which works with all the possible positions that the robots may see.
\end{itemize}





\section{My \emph{Plan} for next week}

\begin{itemize}
\item Complete the algorithm with Mathematica
\item Trying to go to the light by installing Kilobotics platform.(Now our robots don't understand their libraries because of the k-team platform.
\end{itemize}

\subsection{Meeting with Dr. Becker  }

\begin{itemize}
\item To see if my algorithm work and getting comments out of it.
\end{itemize}

\end{document}
