%%%% Weekly Report Information %%%%
\newcommand{\handoutName}{Weekly report}
\newcommand{\handoutdate}{\today}
%\newcommand{\duedate}{}
\input{Header.tex}

\section{My \emph{Objectives} this week}
\begin{itemize}
\item Completing Simulation for 2 robots infinite friction algorithm
\item Upgrading firmware in windows
\item Running go to the light on kilobits
\end{itemize}



\section{My \emph{Accomplishments} this week}

\subsection{\emph{Kilobots}}

\begin{itemize}
\item I finally found how to change kilobots' firmware, I did that for the controller and 31 kilobots, I can now program them.
\item I tried the go to the light program, but it needs some calibration to work. So I am making the code and calibration right now to see if it works or not.
\item Now even with mac we can program the kilobots. (So I removed windows on my machine)
\end{itemize}

\subsection{\emph{Algorithms}}

\begin{itemize}
\item I wrote a draft function that gives the right answer in some cases. But our simulator doesn't work properly and sees errors, I have to fix that to see the result properly but the right path is there. Code is submitted to the github. 
\end{itemize}





\section{My \emph{Plan} for next week}

\begin{itemize}
\item Correcting errors in simulations and apply it to both directions(x,y)
\item Completing code for kilobots.
\item Start working with Arduino and programming the light bulbs.

\end{itemize}

\subsection{Meeting with Dr. Becker  }

\begin{itemize}
\item Unfortunately I have filled a wrong form for my QE. And it seems that I have to fill another form for my PhD committee too. I would appreciate if we could discuss about these forms.
\end{itemize}

\end{document}
