%%%% Weekly Report Information %%%%
\newcommand{\handoutName}{Weekly report}
\newcommand{\handoutdate}{\today}
%\newcommand{\duedate}{}
\input{Header.tex}

\section{My \emph{Objectives} Recently}
\begin{itemize}
\item Completing the table for kilobots
\item Running the experiment of going to light
\end{itemize}



\section{My \emph{Accomplishments} this week}

\subsection{\emph{Kilobots}}

\begin{itemize}
\item We completed the table.
\item I ran the first experiment, but the problem was that kilobots couldn't notice yellow light. When I used my phone light, they could understand it when it was close enough, but when I used yellow light bulbs, they could not understand that. I have bought some white light bulbs to see if it will work for them or not.
\item I wrote the code for Arduino working with matlab, and it works.
\item From the matlab code of finding circles, I extract mean and variance and covariance, and so now everything is ready.

\end{itemize}





\section{My \emph{Plan} for next week}

\begin{itemize}
\item Making webcam steady on the table.
\item Having the experiment of controlling mean with 100 kilobots(We have now all the components we need, I just have to find source of light that robots can see)
\item Going back to Algorithm for using friction. Completing the mathematica code, and go further for more than 2 robots. 
\item Making a demo of the robots following a robot with kilobots.

\end{itemize}

\subsection{Meeting with Dr. Becker  }

\begin{itemize}
\item What are the things I have to achieve for ICRA paper? 
\item How can we make the webcam steady? 
\item Should I meet Dr. Wosik and talk to her about the time of my QE?
\end{itemize}

\end{document}
